EldersAIR: manuscript tables/figures

### 2022-11-02 health_analysis_itt.Rmd
update tables for clinicaltrials.gov reporting

>>>>

tidy_results_primary <- tidy(itt_health_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary")  
  #dplyr::select(-p.value)
kable(tidy_results_primary)

### 2022-11-02 main_analysis_pm.Rmd
update tables for clinicaltrials.gov reporting

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") 
kable(tidy_results_primary)

@@

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary")

>>>>

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 5)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary") 
kable(tidy_results_primary)

@@

tidy_results_primary <- tidy(itt_pm_results_primary, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment", "", term)) %>% 
  mutate(estimate = round((exp(estimate)-1)*100, digits = 2),
         conf.low = round((exp(conf.low)-1)*100, digits = 2),
         conf.high = round((exp(conf.high)-1)*100, digits = 2),
         p.value = round((p.value), digits = 5)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "Primary")

### 2022-11-02 manuscript_tables_figures.Rmd
update tables for clinicaltrials.gov reporting

# summary data for manuscript tables - averaged over multiple Winter 1 visits
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, mean_var) %>% 
  group_by(winter_id) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(home, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  #filter(winter_id == 1) %>% 
  arrange(home, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, treatment, mean_var) %>% 
  group_by(winter_id, treatment) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

>>>>

# summary data for manuscript tables - averaged over multiple Winter 1 visits
num_funct_total <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(adult_id_char, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  filter(winter_id == 2) %>% 
  arrange(adult_id_char, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(adult_id_char, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, mean_var) %>% 
  group_by(winter_id) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}

num_funct_treatment <- function(var, data = elders_cleaned_dataset_by_visit){
demographics_summary <- data %>% 
  #filter(area == "NN") %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  group_by(adult_id_char, winter_id) %>% 
  mutate(mean_var = mean(new_var, na.rm = T)) %>% 
  ungroup() %>% 
  filter(winter_id == 2) %>% 
  arrange(adult_id_char, winter_id, sampling_visit) %>% 
  mutate(new_var = if_else(is.na(new_var), lead(new_var), new_var)) %>% 
  distinct(adult_id_char, winter_id, .keep_all = TRUE) %>% # change this to adult_id_char or home as necessary
  filter(!is.na(mean_var)) %>% 
  dplyr::select(winter_id, treatment, mean_var) %>% 
  group_by(winter_id, treatment) %>% 
  summarize(mean_new_var = mean(mean_var), sd_var = sd(mean_var), n_var = n(), 
            min_var = min(mean_var), med_var = median(mean_var), max_var = max(mean_var))
demographics_summary
}
